---
title: "Plotly by NYC Restaurant Inspection"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

</p>This page aims to discover the patterns of NYC restaurant inspection. I will tidy the "rest_inspec" data and draw a bar plot, a scatter plot, and a box chart regarding to the dataset using plotly package. This page is all about the codes, The plots will be shown in the [flexdashboard](flexdashboard.html) section.</p>
<br>

```{r, message=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)
library(lubridate)
data("rest_inspec")
```

Here is the code for the bar chart. It shows the count of Grade A restaurants in different cuisines. 

```{r}
gradeA_cuisine = rest_inspec |>
  filter(grade == "A") |>
  group_by(cuisine_description) |>
  summarise(count = n()) |>
  plot_ly(x = ~cuisine_description, y = ~count, color = ~cuisine_description, type = "bar", colors = "viridis")

gradeA_cuisine
```

Here is the code for the scatter plot. It shows the count of Grade A restaurants inspected in different year-month.
```{r}
year_count = rest_inspec |>
  filter(grade == "A") |>
  mutate(inspection_date = as.Date(inspection_date),
         year_month = format(inspection_date, format = "%Y-%m")) |>
  group_by(year_month) |>
  summarise(count = n())  |>
  plot_ly(x = ~year_month, y = ~count, color = ~year_month, type = "scatter", mode = "markers", colors = "viridis")

year_count
  
```

Here is the code for the box plot. It gives the information about the restaurant score in respect to different boroughs.

```{r}
boro_score = rest_inspec |>
  drop_na(score, boro) |>
  mutate(boro = fct_reorder(boro, score)) |>
  plot_ly(x = ~boro, y = ~score, color = ~boro, type = "box", colors = "inferno")

boro_score
```

